Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-23 Cover_letter_JPM.tex
Updates from Overleaf

\begin{figure}
%    \centering
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=8cm]{rplot_KMplot_HK1.pdf}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=8cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_signature4_FDRKM.pdf}  
  \end{subfigure}
    \caption{OS in TCGA for a gene signature including HK1, EZR, RRAGA, and DUSP16. Those genes have not significant survival impact if calculated individually.}
    \label{fig:signature4}
\end{figure}

>>>>

Conclusion, we might build a Lasso regression model with L1 regularization to maximize the use of continuous gene expression values (without a cutoff).
The gene signature integrating multiple genes is also a good approach for biomarker discovery.

\begin{figure}
%    \centering
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=8cm]{rplot_KMplot_HK1.pdf}
    \caption{Kaplan-Meier plot}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=8cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_signature4_FDRKM.pdf}  
    \caption{Volcano plot}
  \end{subfigure}

  \caption{(a) OS in TCGA HNSCC for a gene signature including HK1, EZR, RRAGA, and DUSP16; (b) Those genes have not significant survival impact if calculated individually (EZR is not shown on volcano plot due to it's \textit{P} value $>0.05$)}
    \label{fig:signature4}
\end{figure}
